Introduction to Markov state modeling with the PyEMMA software --- v\versionnumber

### 2018-08-29 manuscript/manuscript.tex

We utilize Jupyter~\cite{jupyter} notebooks to show code examples along with figures and interactive widgets to display molecules.
The user can install all necessary packages in one step using the \texttt{conda} command provided by the Anaconda Python stack (\url{https://anaconda.com}).
We recommend Anaconda because it resolves and installs dependencies as well as provides pre-compiled versions of common packages.

The tutorial installation contains a launcher command to start the Jupyter notebook server as well as the notebook files.
The data for the demonstrated test systems is downloaded upon the first use and is cached for future invocations of the tutorial.

The underlying software stack for running the tutorial consists of:
\begin{itemize}
\item \textbf{PyEMMA} -- MSM/HMM estimation, validation, analysis, and visualization, and its dependencies~\cite{pyemma}
\item mdshare -- A downloader for MD data from a public server
\item notebook -- The Jupyter~\cite{jupyter} notebook tool used for running the tutorials, along with extension packages jupyter\_contrib\_nbextensions and nbexamples
\item matplotlib -- A plotting library~\cite{matplotlib}
\item nglview -- Widget for active viewing of molecular structures in Jupyter environments~\cite{nglview}
\end{itemize}

>>>>

We utilize Jupyter~\cite{jupyter} notebooks to show code examples along with figures and interactive widgets to display molecules.
The user can install all necessary packages in one step using the \texttt{conda} command provided by the Anaconda Python stack (\url{https://anaconda.com}).
We recommend Anaconda because it resolves and installs dependencies as well as provides pre-compiled versions of common packages.
The tutorial installation contains a launcher command to start the Jupyter notebook server as well as the notebook files.

You can install the tutorial's dependencies in a new conda environment and start the notebook server via
\begin{verbatim}
conda create -n pyemma_tutorials
conda activate pyemma_tutorials
conda install -c conda-forge pyemma_tutorials
pyemma_tutorials
\end{verbatim}
or refer to \githubrepository{} for more detailed installation and usage instructions.

The data for the demonstrated test systems is downloaded upon the first use and is cached for future invocations of the tutorial.

The underlying software stack for running the tutorial consists of:
\begin{itemize}
\item \textbf{PyEMMA} -- MSM/HMM estimation, validation, analysis, and visualization, and its dependencies~\cite{pyemma}
\item mdshare -- A downloader for MD data from a public server
\item notebook -- The Jupyter~\cite{jupyter} notebook tool used for running the tutorials, along with extension packages jupyter\-\_contrib\_nbextensions and nbexamples
\item matplotlib -- A plotting library~\cite{matplotlib}
\item nglview -- Widget for active viewing of molecular structures in Jupyter environments~\cite{nglview}
\end{itemize}
